Density-dependent selection with strictly relative contests

### 2017-11-17 manuscript.tex
l

Here we compare MacArthur's claims about selection in crowded populations with our density-dependent lottery model.

In the Introduction we gave the essential details of MacArthur's general argument, but we did not specify the role of ``$K$''.

>>>>

In the Introduction we outlined MacArthur's general argument. Here we discuss out some further aspects of

compare MacArthur's claims about selection in crowded populations with our density-dependent lottery model. but did not specify the role of ``$K$''.
